\mytitle

### 2016-08-16 pdocs/thesis/article-section-3.tex
article section 3 tuning continues
article section 3 tuning
article section 3 tuning - constraint parameters

There are currently two alternative six-dof-spring constraint implementations in \bullet\ and 
in this work elastic-plastic versions of both of them were developed. 
Values for elastic-plastic case are shown in tables \ref{tab:epBlockValues}.
Body drops freely during first simulation step and 
gains enough kinetic energy so that higher impulses are needed in few following steps.
This causes plastic strain during next three steps.

@@

Six-dof-spring constraint 2 has feature to avoid unstability by automatically softening constraint
spring if needed.
If this feature is active for elastic-plastic constraint 2.
 \ref{tab:ep2BlockValues}.

\begin {table}[htb!]
\begin{center}
\begin{tabular}{|l|l| l| l|l|l|l|l|}
\hline
{\bf Time} & 
{\bf Location} &
{\it velError} & {\it posError} & {\it rhs} &
{\bf Velocity} & 
{\bf Impulse} & 
{\bf Plastic strain} \\  \hline
0.017... &  0 & -0.17  & 0 & -1000 & 0       & 1000 & 0 \\  \hline
\end {tabular}
\end{center}
\caption {Constraint parameter values for elastic-plastic constraint 2} \label{tab:ep2BlockValues} 
\end {table}

>>>>

There are currently two alternative six-dof-spring constraint implementations in \bullet\ and 
in this work elastic-plastic versions of both of them were developed.

Table  \ref{tab:ep2Parameters} summarizes most significant parameters for this study.
There are also e.g. parameters for controlling joint motors.
Additional equations are created if needed. Enabled springs and motors add one row and
limits add one if upper and lower are same and two if both upper and lower limits are defined.

\begin {table}[htb!]
\begin{center}
\begin{tabular}{|l|l| l| l|l|l|l|l|}
\hline
{\bf Parameter} & 
{\bf Description} 
lowerLimit &  
minimum allowed translation or rotation
 \\  \hline
upperLimit &  
maximum allowed translation or rotation
 \\  \hline
springStiffness & elastic spring stiffness
 \\  \hline
enableSpring & defines if spring is active
 \\  \hline
springStiffnessLimited & should elastic behaviour be tuned to avoid instability
 \\  \hline
equilibriumPoint & should elastic behaviour be tuned to avoid instability
 \\  \hline
currentLimit & describes state of constraint - 0: not limited,
 3: loLimit=hiLimit, 4: current value is between loLimit and HiLimit
 \\ \hline

\end {tabular}
\end{center}
\caption {Selected constraint parameters for elastic-plastic constraint 2} \label{tab:ep2Parameters} 
\end {table}

Values for elastic-plastic case are shown in tables \ref{tab:epBlockValues}.
Body drops freely during first simulation step and 
gains enough kinetic energy so that higher impulses are needed in few following steps.
This causes plastic strain during next three steps.

@@

Six-dof-spring constraint 2 has feature to avoid unstability by automatically softening constraint
spring if needed.
If this feature is active for elastic-plastic constraint 2 constraint it behaves as shown in table
 \ref{tab:ep2BlockValues}.

\begin {table}[htb!]
\begin{center}
\begin{tabular}{|l|l| l| l|l|l|l|l|}
\hline
{\bf Time} & 
{\bf Location} &
{\it velError} & {\it posError} & {\it rhs} &
{\bf Velocity} & 
{\bf Impulse} & 
{\bf Plastic strain} \\  \hline
0.017... &  0 & -0.17  & 2.34 & 13000 & 0       & 1000 & 0 \\  \hline
\end {tabular}
\end{center}
\caption {Constraint parameter values for elastic-plastic constraint 2} \label{tab:ep2BlockValues} 
\end {table}
